|

### 2020-09-14 paper.Rmd
Small fixed to compile pdf.

```{r mouse-cluster, fig.cap = "Selected frames from using a tour of the mouse data with the default tour display (top), and the sage display with $\gamma=3$ (bottom)", fig.width="0.9\\textwidth"}
library(cowplot)
dir <- "pngs/"
frames <- c("001", "016", "038", "074")
draw_panel <- function(png) ggdraw() + 
  draw_image(png) + 
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))

@@

```{r sketches, fig.cap = "Selected frames  of the tour run on the sketches data using the default tour display (top), and using the default sage display (bottom).", fig.width="0.9\\textwidth"}
frames <- c("001", "036", "077", "092")

@@

```{r sketches, fig.cap = "Selected frames of the tour run on the pdfsense data using the default tour display (top), and using the sage display with $R=10$ (bottom)", fig.width="0.9\\textwidth"}
frames <- c("001", "051", "078", "092")

>>>>

```{r mouse-cluster, fig.cap = "Selected frames from using a tour of the mouse data with the default tour display (top), and the sage display with $\\gamma=3$ (bottom)"}
library(cowplot)
dir <- "pngs/"
frames <- c("001", "016", "038", "074")
draw_panel <- function(png) ggdraw() + 
  draw_image(png) + 
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))

@@

```{r sketches, fig.cap = "Selected frames  of the tour run on the sketches data using the default tour display (top), and using the default sage display (bottom)."}
frames <- c("001", "036", "077", "092")

@@

```{r pdfsense, fig.cap = "Selected frames of the tour run on the pdfsense data using the default tour display (top), and using the sage display with $R=10$ (bottom)"}
frames <- c("001", "051", "078", "092")
